Adaptive broadcast tree for multicores

### 2013-05-14 paper.tex
Fixed the include path fro a figure
Added some measurements from real hardware

\begin{figure}
\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
  \pgfsetlinewidth{.5bp}
\input{figs/final_gruyere_hierarchical}
\end{tikzpicture}
\caption{Hierarchical tree for a 8x4x1 multicore. Nodes 0, 4, 8, 12,
  16, 20, 24 and 28 are coordinators. They are arranged in a binary
  tree starting at node 0. Communication within NUMA nodes is
  sequential (as an example: coordinator node 24 sends a message to
  all cores on the same NUMA node, namely 25, 26 and 27)}
\label{fig:gruyere_hierarchy}
\end{figure}

@@

\stefan{These numbers are outdated. Keeping them for reference}

Some numbers are listed in Table~\ref{tab:bc_measurements}.

\begin{table}[htb]
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    broadcast algorithm & \multicolumn{2}{c}{nos5} & \multicolumn{2}{c}{gruyere} \\
      & cycles & error & cycles & error \\
    \midrule
    sequential &  4096.1 &  105.2 & 136751.9 &   3061.5 \\
    batch      &  2408.0 &  181.9 &  57360.8 &   5271.5 \\
    \bottomrule
  \end{tabular}
  \caption{Broadcast measurements}
  \label{tab:bc_measurements}
\end{table}

>>>>

\begin{figure}
\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
  \pgfsetlinewidth{.5bp}
\input{graphs/final_gruyere_hierarchical}
\end{tikzpicture}
\caption{Hierarchical tree for a 8x4x1 multicore. Nodes 0, 4, 8, 12,
  16, 20, 24 and 28 are coordinators. They are arranged in a binary
  tree starting at node 0. Communication within NUMA nodes is
  sequential (as an example: coordinator node 24 sends a message to
  all cores on the same NUMA node, namely 25, 26 and 27)}
\label{fig:gruyere_hierarchy}
\end{figure}

@@

\paragraph{Binary tree on sbrinz2}

Plot~\ref{pgfplot:201305101058} shows the time in cycles until a
message send from core $n$ is received back via the broadcast tree
show in Figure~\ref{fig:binary_tree_sbrinz2}. We were expecting
increasing cost with the depth of the tree. If a message is sent from
one of the leave nodes, it takes longer to receive this message back
on the tree.

The result is quite unexpected. We would expect nodes far down in the
tree to experience a longer waiting time for receiving own messages
back on the tree (due to more hops). This observation does not seem to
be true.

Lukas Humbel, who was also working on sbrinz1 was observing that the
Barrelfish core IDs might not properly correspond to physical core
IDs. This could explain the numbers we observe in our measurement.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{binary_tree_sbrinz2}
  \caption{Binary tree for sbrinz2}
  \label{fig:binary_tree_sbrinz2}
\end{figure}

\begin{figure}
  \caption{Cost for receiving a message back on the tree. This is the
    time for which the send call needs to be blocked to retain atomic
    broadcast properties.}
  \label{pgfplot:201305101058}
  \begin{tikzpicture}
    \begin{axis}[%
        xlabel=sender core ID,%
        ylabel={Cost [cycles]}%
        ]
    \addplot[%
        color=red,%
        mark=x,%  
        error bars/y dir=both,%
        error bars/y explicit%
        ] coordinates {
      (1,276.1) +- (291.3,291.3)
      (2,876.1) +- (56.6,56.6)
      (3,863.0) +- (108.3,108.3)
      (4,899.7) +- (102.3,102.3)
      (5,893.5) +- (44.5,44.5)
      (6,880.5) +- (39.4,39.4)
      (7,520.9) +- (41.7,41.7)
      (8,171.9) +- (91.5,91.5)
      (9,155.7) +- (51.4,51.4)
      (10,174.6) +- (99.9,99.9)
      (11,175.1) +- (99.3,99.3)
      (12,154.5) +- (50.5,50.5)
      (13,176.8) +- (109.7,109.7)
      (14,173.1) +- (99.4,99.4)
      (15,150.4) +- (43.3,43.3)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

\paragraph{Older numbers}
